\section{Theoretical Background}
\label{sec:theoretical-background}

This chapter defines the physical configuration, governing equations, and
turbulence statistics required for the present work. It first establishes the
incompressible, non-buoyant channel-flow baseline; thermal stratification will
be introduced later.

\subsection{Governing Equations and Physical Configuration}
\label{sec:channel-flow-governing-equations}

Plane channel flow consists of fluid motion between two stationary, parallel
walls separated by the full channel height $2\delta$, where $\delta$ is the
channel half-height. The coordinates $x$, $y$, and $z$ denote the streamwise,
spanwise, and wall-normal directions, respectively. The corresponding
instantaneous velocity components are $u$, $v$, and $w$, and the velocity
vector is $\mathbf{u}=(u,v,w)$. Figure~\ref{fig:channel-geometry} shows the
coordinate convention used in this chapter.

\begin{figure}[htbp]
  \centering
  \setlength{\unitlength}{1mm}
  \begin{picture}(120,46)
    \put(12,8){\line(1,0){96}}
    \put(12,36){\line(1,0){96}}
    \put(15,3){stationary wall, $z=-\delta$}
    \put(15,39){stationary wall, $z=\delta$}
    \put(43,22){\vector(1,0){30}}
    \put(75,20){$x$}
    \put(43,22){\vector(0,1){11}}
    \put(39,33){$z$}
    \put(43,22){\circle*{1.2}}
    \put(38,17){$y$ out of the page}
    \put(86,22){\vector(1,0){15}}
    \put(88,25){mean flow}
  \end{picture}
  \caption{Plane-channel configuration: $x$ is streamwise, $y$ is spanwise
  (out of the page), and $z$ is wall-normal.}
  \label{fig:channel-geometry}
\end{figure}

\subsubsection{Conservation of Mass}

For an incompressible fluid of constant density, conservation of mass reduces
to
\begin{equation}
  \boldsymbol{\nabla}\mathbin{\cdot}\mathbf{u}=0,
  \label{eq:incompressible-continuity}
\end{equation}
where $\boldsymbol{\nabla}$ is the spatial gradient operator. Equation
\eqref{eq:incompressible-continuity} requires the velocity field to be
divergence-free and expresses local conservation of fluid mass.

\subsubsection{Conservation of Momentum}

The present formulation treats the fluid as Newtonian, with constant density
$\rho$ and constant kinematic viscosity $\nu$. Conservation of momentum is
then described by the incompressible Navier--Stokes equations,
\begin{equation}
  \frac{\partial \mathbf{u}}{\partial t}
  +(\mathbf{u}\mathbin{\cdot}\boldsymbol{\nabla})\mathbf{u}
  =-\frac{1}{\rho}\boldsymbol{\nabla}p
  +\nu\boldsymbol{\nabla}^{2}\mathbf{u},
  \label{eq:incompressible-navier-stokes}
\end{equation}
where $t$ is time, $p$ is pressure, and $\boldsymbol{\nabla}^{2}$ is the
Laplace operator. In SI units, $\rho$, $\nu$, and $p$ are measured in
$\mathrm{kg\,m^{-3}}$, $\mathrm{m^2\,s^{-1}}$, and pascals, respectively.
The two terms on the left-hand side represent local and convective
acceleration; the right-hand side contains pressure acceleration and viscous
momentum diffusion \cite{pope2000}.

\subsubsection{Pressure-Gradient Forcing}

A streamwise pressure gradient maintains the channel flow. The pressure is
written as a linear mean contribution plus a periodic remainder
$\widetilde{p}$,
\begin{equation}
  p(x,y,z,t)=-Gx+\widetilde{p}(x,y,z,t),
  \qquad
  G=-\frac{\mathrm{d}\langle p\rangle}{\mathrm{d}x}>0,
  \label{eq:channel-pressure-decomposition}
\end{equation}
where $G$ is the imposed streamwise pressure drop per unit length in
$\mathrm{Pa\,m^{-1}}$, and angle brackets denote a statistical average.
Substitution into Eq.~\eqref{eq:incompressible-navier-stokes} gives
\begin{equation}
  \frac{\partial \mathbf{u}}{\partial t}
  +(\mathbf{u}\mathbin{\cdot}\boldsymbol{\nabla})\mathbf{u}
  =-\frac{1}{\rho}\boldsymbol{\nabla}\widetilde{p}
  +\nu\boldsymbol{\nabla}^{2}\mathbf{u}
  +\frac{G}{\rho}\mathbf{e}_x,
  \label{eq:pressure-driven-navier-stokes}
\end{equation}
where $\mathbf{e}_x$ is the unit vector in the positive streamwise direction.
The final term is the uniform acceleration associated with the mean pressure
gradient. Equation~\eqref{eq:pressure-driven-navier-stokes} defines the
physical forcing considered here; its implementation by the solver is not
specified at this stage.

\subsubsection{Computational Domain and Boundary Conditions}

The walls are located at $z=-\delta$ and $z=\delta$. Impermeability and the
no-slip condition require
\begin{equation}
  \mathbf{u}(x,y,-\delta,t)
  =\mathbf{u}(x,y,\delta,t)=\mathbf{0}.
  \label{eq:channel-no-slip}
\end{equation}
The zero vector in Eq.~\eqref{eq:channel-no-slip} states that all three
velocity components vanish at each stationary wall. For a channel domain of
streamwise length $L_x$ and spanwise length $L_y$, periodicity in the two
wall-parallel directions is expressed as
\begin{equation}
  \mathbf{u}(x+L_x,y,z,t)=\mathbf{u}(x,y,z,t),
  \qquad
  \mathbf{u}(x,y+L_y,z,t)=\mathbf{u}(x,y,z,t).
  \label{eq:channel-periodicity}
\end{equation}
These conditions represent a repeating section of the channel and make $x$
and $y$ statistically homogeneous. The instantaneous flow remains
three-dimensional and time-dependent \cite{kimMoinMoser1987}.

\subsubsection{Fully Developed Channel Flow}

Fully developed channel flow is defined statistically: its mean quantities do
not vary in the homogeneous directions. The mean velocity therefore has the
form
\begin{equation}
  \langle\mathbf{u}\rangle=\bigl(U(z),0,0\bigr),
  \label{eq:fully-developed-channel-flow}
\end{equation}
where $U(z)=\langle u\rangle$ is the mean streamwise velocity. Equation
\eqref{eq:fully-developed-channel-flow} describes the mean field only and does
not imply that the instantaneous turbulent field is steady.

\subsection{Turbulence Statistics for Validation}
\label{sec:reynolds-decomposition-turbulence-statistics}

Validation of a turbulent channel calculation is based on converged
statistics rather than individual instantaneous fields. The quantities needed
for the present work are defined below using the coordinate convention of
Subsection~\ref{sec:channel-flow-governing-equations}.

\subsubsection{Reynolds Decomposition and Averaging}

The instantaneous velocity is separated into mean and fluctuating parts by the
Reynolds decomposition,
\begin{equation}
  u_i(\mathbf{x},t)=U_i(\mathbf{x})+u_i'(\mathbf{x},t),
  \qquad
  U_i=\langle u_i\rangle,
  \qquad i\in\{1,2,3\},
  \label{eq:reynolds-decomposition}
\end{equation}
where $\mathbf{x}=(x,y,z)$ is the position vector, $u_i$ is an instantaneous
velocity component, $U_i$ is its mean, $u_i'$ is its fluctuation, and $i$ is
the component index. The assignments $u_1=u$, $u_2=v$, and $u_3=w$ correspond
to the streamwise, spanwise, and wall-normal components. In component form,
$u=U+u'$, $v=V+v'$, and $w=W+w'$, where $U=\langle u\rangle$,
$V=\langle v\rangle$, and $W=\langle w\rangle$. All velocity quantities have
units of $\mathrm{m\,s^{-1}}$. For the fully developed flow in
Eq.~\eqref{eq:fully-developed-channel-flow}, $U=U(z)$ and $V=W=0$. The
fluctuations satisfy
\begin{equation}
  \langle u_i'\rangle=0,
  \qquad
  \langle u'\rangle=\langle v'\rangle=\langle w'\rangle=0.
  \label{eq:zero-mean-velocity-fluctuations}
\end{equation}
Equation~\eqref{eq:zero-mean-velocity-fluctuations} follows directly from the
definition of the mean \cite{pope2000}.

For an instantaneous flow quantity $\phi$, the ideal time average is
\begin{equation}
  \langle\phi\rangle_t(x,y,z)
  =\lim_{T\rightarrow\infty}\frac{1}{T}
  \int_{t_0}^{t_0+T}\phi(x,y,z,t)\,\mathrm{d}t,
  \label{eq:turbulence-time-average}
\end{equation}
where $t_0$ is the start of the sampling interval and $T$ is its duration in
seconds. In a statistically stationary calculation, the converged result is
independent of $t_0$. Averaging additionally over the homogeneous directions
gives
\begin{equation}
  \langle\phi\rangle(z)
  =\frac{1}{L_xL_y}\int_0^{L_y}\int_0^{L_x}
  \langle\phi\rangle_t(x,y,z)\,\mathrm{d}x\,\mathrm{d}y.
  \label{eq:channel-space-time-average}
\end{equation}
Equation~\eqref{eq:channel-space-time-average} is the statistical average used
below. For finite simulation data, the sampling interval must be long enough
for each reported quantity to converge. Under an ergodic interpretation, this
space--time average estimates the corresponding ensemble average. Statistical
stationarity refers to the statistics, not to a steady instantaneous field.

The second moments are collected in the kinematic Reynolds-stress tensor,
\begin{equation}
  R_{ij}(z)=\langle u_i'u_j'\rangle,
  \label{eq:reynolds-stress-tensor}
\end{equation}
where $R_{ij}$ has units of $\mathrm{m^2\,s^{-2}}$. The diagonal components
$R_{11}$, $R_{22}$, and $R_{33}$ are the streamwise, spanwise, and wall-normal
normal stresses; the off-diagonal components describe correlations between
different velocity fluctuations.

\subsubsection{RMS Velocity Fluctuations}

The root-mean-square (RMS) velocity fluctuations are
\begin{equation}
  u_{\mathrm{rms}}(z)=\sqrt{\langle u'^2\rangle},
  \qquad
  v_{\mathrm{rms}}(z)=\sqrt{\langle v'^2\rangle},
  \qquad
  w_{\mathrm{rms}}(z)=\sqrt{\langle w'^2\rangle}.
  \label{eq:rms-velocity-fluctuations}
\end{equation}
These quantities are the square roots of $R_{11}$, $R_{22}$, and $R_{33}$,
respectively, and have units of $\mathrm{m\,s^{-1}}$. Their profiles measure
the typical streamwise, spanwise, and wall-normal fluctuation magnitudes across
the channel and are standard quantities for comparison with reference DNS data
\cite{kimMoinMoser1987}.

\subsubsection{Reynolds Shear Stress}

The Reynolds-stress component relevant to wall-normal transport of streamwise
momentum is
\begin{equation}
  -R_{13}(z)=-\langle u'w'\rangle.
  \label{eq:reynolds-shear-stress}
\end{equation}
Here, $u'$ and $w'$ are the streamwise and wall-normal velocity fluctuations.
The kinematic stress in Eq.~\eqref{eq:reynolds-shear-stress} has units of
$\mathrm{m^2\,s^{-2}}$; multiplication by $\rho$ gives the dimensional
turbulent shear stress $-\rho\langle u'w'\rangle$ in pascals. This correlation
quantifies turbulent momentum transfer between wall-parallel layers and is a
central validation quantity for channel flow \cite{pope2000}.

\subsubsection{Turbulent Kinetic Energy}

The turbulent kinetic energy per unit mass is
\begin{equation}
  k(z)=\frac{1}{2}\langle u_i'u_i'\rangle
  =\frac{1}{2}\left(
    \langle u'^2\rangle+\langle v'^2\rangle+\langle w'^2\rangle
  \right),
  \label{eq:turbulent-kinetic-energy}
\end{equation}
where a repeated index denotes summation over the three Cartesian components.
The quantity $k$ is the mean kinetic energy of the velocity fluctuations per
unit fluid mass. Its SI units are $\mathrm{m^2\,s^{-2}}$, equivalently
$\mathrm{J\,kg^{-1}}$.

\subsubsection{Validation Quantities for the Present Work}

The present work will later extract the mean streamwise velocity $U(z)$, the
three RMS velocity fluctuations, the Reynolds shear stress
$-\langle u'w'\rangle$, and the turbulent kinetic energy $k(z)$ from BRINE.
Their definitions are independent of the solver implementation, but the
coordinate mapping and sampling procedure must be confirmed before the output
is processed. Agreement with trusted non-buoyant channel DNS data is required
before differences caused by buoyancy are interpreted.

\subsection{Wall Scaling, Friction Reynolds Number, and Law of the Wall}
\label{sec:wall-scaling-law-wall}

Wall scaling relates the near-wall velocity field to the shear exerted by a
solid boundary. For the mean streamwise velocity $U(z)$ defined in
Eq.~\eqref{eq:fully-developed-channel-flow}, the positive magnitude of the wall
shear stress is
\begin{equation}
  \tau_w
  =\mu\left|\frac{\mathrm{d}U}{\mathrm{d}z}\right|_w
  =\rho\nu\left|\frac{\mathrm{d}U}{\mathrm{d}z}\right|_w,
  \label{eq:wall-shear-stress}
\end{equation}
where the subscript $w$ denotes evaluation at either wall, $\mu=\rho\nu$ is
the dynamic viscosity, and $\nu$ is the kinematic viscosity introduced in
Eq.~\eqref{eq:incompressible-navier-stokes}. The absolute value removes the
opposite gradient signs at the lower and upper walls. Physically, $\tau_w$ is
the streamwise force transmitted per unit wall area; its SI unit is the pascal,
$\mathrm{Pa}=\mathrm{N\,m^{-2}}$.

The corresponding friction velocity, channel half-height, and friction
Reynolds number are
\begin{equation}
  u_\tau=\sqrt{\frac{\tau_w}{\rho}},
  \qquad
  h=\frac{L_z}{2},
  \qquad
  Re_\tau=\frac{u_\tau h}{\nu}.
  \label{eq:friction-scaling-quantities}
\end{equation}
Here, $u_\tau$ has units of velocity but is a shear-based scaling quantity, not
the local fluid velocity. The half-height $h$ is identical to $\delta$ in the
centred geometry of Fig.~\ref{fig:channel-geometry}, and $L_z$ is the full
wall-normal channel length. The parameter $Re_\tau$ measures the separation
between the outer length $h$ and the near-wall viscous length; increasing
$Re_\tau$ generally increases the range of dynamically relevant wall-turbulence
scales \cite{pope2000}.

The planned project convention uses $L_z=2$, $|\Pi|=1$, and $\rho=1$, where
$\Pi=\mathrm{d}\langle p\rangle/\mathrm{d}x=-G$ is the signed mean pressure
gradient associated with Eq.~\eqref{eq:channel-pressure-decomposition}. For a
fully developed plane channel, the mean streamwise momentum balance gives
$\tau_w=h|\Pi|$. Consequently,
\begin{equation}
  h=1,
  \qquad
  \tau_w=1,
  \qquad
  u_\tau=1,
  \qquad
  \nu=\mu=\frac{1}{Re_\tau}
  \quad (\rho=1).
  \label{eq:project-wall-scaling-normalization}
\end{equation}
Equation~\eqref{eq:project-wall-scaling-normalization} documents the intended
nondimensional setup. It is not a result from a completed simulation.

Let $d_w$ be the non-negative distance from a point to the nearest wall. In the
centred coordinate system of Fig.~\ref{fig:channel-geometry},
$d_w=h-|z|$; for data stored on $0\leq z\leq L_z$, the equivalent expression is
$d_w=\min(z,L_z-z)$. The viscous length, wall distance, and mean velocity in
wall units are
\begin{equation}
  \ell_\nu=\frac{\nu}{u_\tau},
  \qquad
  z^+=\frac{d_w}{\ell_\nu}=\frac{d_wu_\tau}{\nu},
  \qquad
  U^+=\frac{U}{u_\tau}.
  \label{eq:viscous-length-wall-units}
\end{equation}
The RMS quantities from Eq.~\eqref{eq:rms-velocity-fluctuations} and the
Reynolds shear stress from Eq.~\eqref{eq:reynolds-shear-stress} are scaled as
\begin{equation}
  \begin{aligned}
    u_{\mathrm{rms}}^+&=\frac{u_{\mathrm{rms}}}{u_\tau},
    &v_{\mathrm{rms}}^+&=\frac{v_{\mathrm{rms}}}{u_\tau},
    &w_{\mathrm{rms}}^+&=\frac{w_{\mathrm{rms}}}{u_\tau},\\
    -\langle u'w'\rangle^+
    &=-\frac{\langle u'w'\rangle}{u_\tau^2}
    =\frac{-\rho\langle u'w'\rangle}{\tau_w}.
  \end{aligned}
  \label{eq:inner-scaled-turbulence-statistics}
\end{equation}

BRINE uses $z$ and $w$ for the wall-normal coordinate and velocity component,
respectively. Much of the wall-turbulence literature instead uses $y$ as the
wall-normal coordinate and therefore denotes wall distance by $y^+$. That
conventional symbol may be retained in comparison figures only when it is
defined explicitly as distance from the nearest wall in wall units. It must not
be confused with the BRINE coordinate $y$, which is spanwise, or with the
spanwise velocity $v$. The same mapping converts a literature stress
$-\langle u'v'\rangle$ into the BRINE quantity $-\langle u'w'\rangle$ when the
reference uses $v$ for wall-normal velocity.

The near-wall flow is commonly described using four approximate regions. In
the viscous sublayer, molecular viscosity dominates the mean momentum transfer.
The buffer layer is a transition in which viscous and turbulent effects are
both important. Farther from the wall, the logarithmic or overlap region links
inner and outer scaling, whereas the outer region is influenced by the channel
half-height, pressure-gradient forcing, and centreline conditions. These
regions do not have universal sharp boundaries; their extent depends in part
on Reynolds number \cite{pope2000}.

For a smooth wall, the leading inner relation in the viscous sublayer is
\begin{equation}
  U^+=z^+.
  \label{eq:viscous-law-of-wall}
\end{equation}
In the logarithmic overlap region, the generic law of the wall is
\begin{equation}
  U^+=\frac{1}{\kappa_{\mathrm{vK}}}\ln(z^+)+B,
  \label{eq:logarithmic-law-of-wall}
\end{equation}
where $\kappa_{\mathrm{vK}}$ is the dimensionless von K\'arm\'an constant and
$B$ is the additive intercept. The symbol $\kappa_{\mathrm{vK}}$ is distinct
from the thermal diffusivity $\kappa$, which has units of
$\mathrm{m^2\,s^{-1}}$. No project-specific numerical values are assigned to
$\kappa_{\mathrm{vK}}$ or $B$ at this stage \cite{pope2000}.

Wall-unit profiles provide a common basis for comparing channel calculations
at a specified $Re_\tau$. The planned unstratified benchmark at $Re_\tau=590$
will therefore compare $U^+$, the three RMS fluctuations in
Eq.~\eqref{eq:inner-scaled-turbulence-statistics}, and the inner-scaled
Reynolds shear stress with established channel-DNS statistics
\cite{kimMoinMoser1987,moserKimMansour1999}. This comparison extends the
validation quantities
identified in Subsection~\ref{sec:reynolds-decomposition-turbulence-statistics};
it defines a future validation procedure and does not imply that validation has
already been completed.

\subsection{Passive Scalar and Temperature Transport}
\label{sec:passive-scalar-temperature-transport}

A scalar field $\theta(\mathbf{x},t)$ can represent temperature when density
feedback is disabled. Such a scalar is passive: it is transported by the
velocity field but does not modify the momentum equation. An active scalar, by
contrast, changes the momentum balance through a coupling such as buoyancy.
The detailed active-buoyancy formulation is introduced separately from the
passive transport considered here.

For constant molecular diffusivity, the dimensional advection--diffusion
equation is
\begin{equation}
  \frac{\partial\theta}{\partial t}
  +\mathbf{u}\mathbin{\cdot}\boldsymbol{\nabla}\theta
  =\kappa\boldsymbol{\nabla}^{2}\theta+Q,
  \label{eq:passive-scalar-transport}
\end{equation}
where $\mathbf{u}$ is the instantaneous velocity from
Eq.~\eqref{eq:incompressible-navier-stokes}, $\kappa$ is the molecular scalar
diffusivity, and $Q$ is a local volumetric scalar source expressed per unit
fluid capacity. The second term on the left of
Eq.~\eqref{eq:passive-scalar-transport} is advection by the flow, whereas the
first and second terms on the right describe molecular diffusion and source
production, respectively. If $\theta$ is temperature, its SI unit is kelvin,
$\kappa$ has units of $\mathrm{m^2\,s^{-1}}$, and $Q$ has units of
$\mathrm{K\,s^{-1}}$; every term in the equation then has units of
$\mathrm{K\,s^{-1}}$. A physical heat-generation rate in
$\mathrm{W\,m^{-3}}$ must first be divided by the volumetric heat capacity to
obtain this form. Equation~\eqref{eq:passive-scalar-transport} may also be
nondimensionalised, but its scales and the resulting source definition must
then be stated explicitly \cite{pope2000}.

The Prandtl number is
\begin{equation}
  Pr=\frac{\nu}{\kappa},
  \label{eq:prandtl-number}
\end{equation}
where $\nu$ is the kinematic viscosity defined in
Eq.~\eqref{eq:incompressible-navier-stokes}. It is the ratio of molecular
momentum diffusivity to molecular thermal diffusivity. Momentum and scalar
diffuse at the same molecular rate when $Pr=1$; scalar diffusion is faster
when $Pr<1$, whereas momentum diffusion is faster relative to scalar diffusion
when $Pr>1$.

Using the Reynolds decomposition in Eq.~\eqref{eq:reynolds-decomposition} as
an analogue, the instantaneous scalar is written as
\begin{equation}
  \theta(\mathbf{x},t)=\Theta(z)+\theta'(\mathbf{x},t),
  \qquad
  \Theta(z)=\langle\theta\rangle,
  \qquad
  \langle\theta'\rangle=0,
  \label{eq:scalar-reynolds-decomposition}
\end{equation}
where $\Theta$ is the mean scalar profile and $\theta'$ is the scalar
fluctuation. The angle brackets denote the space--time average over the
homogeneous $x$ and $y$ directions defined in
Eq.~\eqref{eq:channel-space-time-average}. In addition to $\Theta$, the
principal scalar statistics are
\begin{equation}
  \begin{aligned}
    \sigma_\theta^2(z)&=\langle\theta'^2\rangle,
    &\theta_{\mathrm{rms}}(z)&=\sqrt{\sigma_\theta^2}
      =\sqrt{\langle\theta'^2\rangle},\\
    F_{\theta,z}(z)&=\langle w'\theta'\rangle.
  \end{aligned}
  \label{eq:scalar-validation-statistics}
\end{equation}
The mean profile gives the average scalar distribution across the channel,
$\sigma_\theta^2$ is the scalar variance, and $\theta_{\mathrm{rms}}$ gives the
characteristic fluctuation amplitude in the same units as $\theta$. The
turbulent flux $F_{\theta,z}=\langle w'\theta'\rangle$ quantifies scalar
transport by wall-normal turbulent motion and has units of scalar times
$\mathrm{m\,s^{-1}}$. Here, $w$ is BRINE's wall-normal velocity component;
$v$ remains the spanwise component.

Scalar boundary conditions specify either the wall value, its outward-normal
gradient, or a combination of both. A general linear condition is
\begin{equation}
  a\theta+b\frac{\partial\theta}{\partial n}=c
  \qquad\text{on a wall},
  \label{eq:scalar-wall-boundary-condition}
\end{equation}
where $n$ is the outward unit-normal direction and the coefficients $a$, $b$,
and $c$ carry the units required for dimensional consistency. A prescribed
scalar value is a Dirichlet condition, represented by $a=1$ and $b=0$. A
prescribed scalar flux is a Neumann condition; the insulated zero-flux case is
$a=0$, $b=1$, and $c=0$. Non-zero $a$ and $b$ give a mixed or Robin condition.
These mathematical forms do not identify BRINE input-line values, which must
be checked from the approved case input before use.

\paragraph{Official project benchmark.}
The current project roadmap specifies a planned case at $Re_\tau=550$ and
$Pr=1$, with buoyancy disabled, constant isothermal walls $\theta=0$, and
uniform internal heating $Q=1/Pr$ in the nondimensional scalar equation. The
intended comparisons include the mean temperature in wall units and the
temperature RMS. This is a planned benchmark rather than a completed result;
the separately recorded inconsistency between $Re_\tau=550$ and
$Re_\tau=500$ must be resolved before the case is configured or run.

\paragraph{Kleandro working reference.}
The separate working reference uses $Re_\tau=150$, $Pr=1$, and disabled
buoyancy, with opposed fixed nondimensional wall values $\theta=+1$ at the
lower wall and $\theta=-1$ at the upper wall. It is useful for understanding
the thermal workflow and post-processing, but it is not the official
$Re_\tau=550$ reproduction case. Its parameters and normalization must not be
combined with those of the internally heated benchmark.

For a generic scalar, the outward-normal component of the molecular scalar
flux and its friction-scalar scale may be defined as
\begin{equation}
  j_w=-\kappa\left.\frac{\partial\Theta}{\partial n}\right|_w,
  \qquad
  \theta_\tau=\frac{|j_w|}{u_\tau},
  \qquad
  \Delta\Theta^+
  =s_w\frac{\Theta_w-\Theta}{\theta_\tau},
  \label{eq:scalar-wall-scaling}
\end{equation}
where $\Theta_w$ is the mean wall scalar and $u_\tau$ is the friction velocity
from Eq.~\eqref{eq:friction-scaling-quantities}. If $\theta$ is temperature,
$j_w$ has units of $\mathrm{K\,m\,s^{-1}}$ and $\theta_\tau$ has units of
kelvin; $j_w$ is therefore a kinematic scalar flux rather than a heat flux in
$\mathrm{W\,m^{-2}}$. The factor $s_w\in\{-1,+1\}$ records the chosen sign
orientation and is selected separately at each wall so that the plotted
$\Delta\Theta^+$ has the stated direction. This convention must be reported
rather than assumed for the final BRINE benchmark. Wall distance is scaled by
the same $z^+$ defined in Eq.~\eqref{eq:viscous-length-wall-units}.

Like the mean velocity, a passive-scalar profile can contain a near-wall
conductive region, an overlap region, and a core region. The leading
near-wall behaviour is linear under appropriate inner scaling. A generic
scalar logarithmic relation in the overlap region is
\begin{equation}
  \Delta\Theta^+
  =\frac{1}{\kappa_\theta}\ln(z^+)+B_\theta,
  \label{eq:scalar-logarithmic-law}
\end{equation}
where $\kappa_\theta$ is a dimensionless scalar logarithmic-law constant and
$B_\theta$ is its additive intercept. The symbol $\kappa_\theta$ is distinct
from the thermal diffusivity $\kappa$ in
Eq.~\eqref{eq:passive-scalar-transport} and from the von K\'arm\'an velocity
constant $\kappa_{\mathrm{vK}}$ in
Eq.~\eqref{eq:logarithmic-law-of-wall}. The region boundaries and the constants
depend on the scalar boundary condition and normalization; no numerical values
are assigned here \cite{pope2000}.

Future passive-scalar validation should compare the mean scalar profile,
$\theta_{\mathrm{rms}}$, the wall scalar gradient or flux where available,
relevant inner-scaled profiles, and, where reported, the turbulent scalar flux
$\langle w'\theta'\rangle$. A strict comparison requires compatible
$Re_\tau$, $Pr$, wall boundary conditions, scalar forcing, normalization, and
averaging interval. Any coordinate remapping, profile folding,
symmetrization, or interpolation must also be disclosed. A non-twin reference
can support qualitative or semi-quantitative assessment, but not strict
validation.

\subsection{Boussinesq Approximation and Thermal Buoyancy}
\label{sec:boussinesq-thermal-buoyancy}

Temperature becomes an active scalar when its associated density variation
produces a force in the momentum balance. The transport equation
\eqref{eq:passive-scalar-transport} remains necessary, but the dependence is
then two-way: the velocity field advects temperature, while temperature
modifies the velocity through buoyancy.

For modest temperature differences, the Boussinesq approximation linearises
density about a reference state as
\begin{equation}
  \rho(\theta)
  =\rho_0\left[1-\alpha_T(\theta-\theta_0)\right],
  \label{eq:boussinesq-density-temperature}
\end{equation}
where $\rho_0$ is the reference density, $\theta_0$ is the reference
temperature, and $\alpha_T$ is the thermal-expansion coefficient in
$\mathrm{K^{-1}}$. For an ordinary fluid with $\alpha_T>0$, increasing
temperature decreases density. The coefficient $\alpha_T$ is a thermodynamic
property and is distinct from the thermal diffusivity $\kappa$ in
Eq.~\eqref{eq:passive-scalar-transport}.

The approximation assumes that relative density changes are small. Density is
therefore set to $\rho_0$ in continuity, inertia, and the viscous terms, and is
allowed to vary only in the gravitational contribution. The velocity remains
approximately divergence-free as in
Eq.~\eqref{eq:incompressible-continuity}. This model is not appropriate when
density changes are too large for the linear relation in
Eq.~\eqref{eq:boussinesq-density-temperature} to remain accurate
\cite{pope2000}.

Let $\mathbf{g}$ be the physical gravitational-acceleration vector, pointing
in the direction in which gravity acts. Its magnitude is
$g=|\mathbf{g}|$. After the uniform reference contribution $\mathbf{g}$ has
been absorbed into the hydrostatic pressure, the remaining thermal buoyancy
acceleration is
\begin{equation}
  \mathbf{f}_b
  =\frac{\rho-\rho_0}{\rho_0}\mathbf{g}
  =-\alpha_T(\theta-\theta_0)\mathbf{g}.
  \label{eq:boussinesq-buoyancy-acceleration}
\end{equation}
With this convention, a warm perturbation for which
$\theta-\theta_0>0$ accelerates opposite to $\mathbf{g}$, whereas a cold
perturbation accelerates along $\mathbf{g}$. Other formulations may reverse
the displayed sign by defining an upward gravity vector, a buoyancy variable,
or a nondimensional temperature with the opposite orientation. The sign must
therefore be interpreted together with the direction of $\mathbf{g}$, the
definition of $\theta$, and the chosen reference state.

Adding Eq.~\eqref{eq:boussinesq-buoyancy-acceleration} to the pressure-driven
momentum equation gives
\begin{equation}
  \frac{\partial \mathbf{u}}{\partial t}
  +(\mathbf{u}\mathbin{\cdot}\boldsymbol{\nabla})\mathbf{u}
  =-\frac{1}{\rho_0}\boldsymbol{\nabla}\widetilde{p}_b
  +\nu\boldsymbol{\nabla}^{2}\mathbf{u}
  +\frac{G}{\rho_0}\mathbf{e}_x
  -\alpha_T(\theta-\theta_0)\mathbf{g},
  \label{eq:boussinesq-pressure-driven-momentum}
\end{equation}
where $\widetilde{p}_b$ is the dynamic pressure remainder after the reference
hydrostatic contribution has been removed. The pressure-gradient term
$G\mathbf{e}_x/\rho_0$ maintains the mean streamwise flow. The final term is
the thermal buoyancy acceleration. Equations
\eqref{eq:passive-scalar-transport} and
\eqref{eq:boussinesq-pressure-driven-momentum} form the coupled thermal-flow
system under the stated assumptions.

For BRINE, the advisor-confirmed conceptual information is limited to the
following: temperature transport is controlled through a temperature flag;
salinity and melting remain disabled for the present Master Project; and the
thermal buoyancy coupling is proportional to temperature through a coefficient
described as an alpha--gravity-type term. The exact variable spelling, input
location, nondimensional coefficient, and implemented sign have not yet been
verified in the active code version and are not specified here. Salinity could
provide an additional density contribution in a more general model, but it is
outside the present project and no double-diffusive formulation is developed.

\subsection{Stable Thermal Stratification}
\label{sec:stable-thermal-stratification}

Thermal stratification describes how buoyancy varies along the gravity
direction. A stable arrangement places the fluid in a local minimum of
gravitational potential energy: a displaced parcel experiences a restoring
tendency. In an unstable arrangement, buoyancy amplifies a displacement and
convection may develop. A neutral arrangement has no leading restoring or
amplifying buoyancy effect. These statements depend on the density gradient
relative to gravity, not on a universal assignment of hot and cold channel
walls. The wall temperatures and gravity sign for the BRINE benchmark must be
taken from the approved input before a wall orientation is stated.

For a sign-explicit definition, let $s$ increase opposite to
$\mathbf{g}$, so gravitational potential energy increases with $s$. The
squared Brunt--V\"ais\"al\"a or buoyancy frequency is then defined by
\begin{equation}
  N^2
  =-\frac{g}{\rho_0}\frac{\mathrm{d}\overline{\rho}}{\mathrm{d}s}
  =g\alpha_T\frac{\mathrm{d}\Theta}{\mathrm{d}s},
  \label{eq:brunt-vaisala-frequency}
\end{equation}
where $\overline{\rho}(s)$ is the mean density and $\Theta(s)$ is the mean
dimensional temperature from the decomposition in
Eq.~\eqref{eq:scalar-reynolds-decomposition}, expressed along $s$. The second
equality follows only from the dimensional linear density law in
Eq.~\eqref{eq:boussinesq-density-temperature}. The quantity $N^2$ has units of
$\mathrm{s^{-2}}$. Under the adopted convention, $N^2>0$ is stable,
$N^2=0$ is neutral, and $N^2<0$ is unstable. If BRINE transports a
nondimensional scalar, its temperature scale and sign must be included before
Eq.~\eqref{eq:brunt-vaisala-frequency} is applied \cite{pope2000}.

Mean shear transfers energy into turbulent motion, whereas stable buoyancy
opposes wall-normal displacement. Increasing stable stratification can
therefore weaken turbulent mixing, make momentum and scalar transport more
anisotropic, reduce turbulence in the channel core, and promote wave-like
motion. The balance varies across the channel because both shear and
stratification are spatially non-uniform
\cite{armenioSarkar2002,garciaVillalbaDelAlamo2011}.

When the stratification and mean-shear gradients are both aligned with the
BRINE wall-normal coordinate $z$, their local competition can be measured by
the gradient Richardson number
\begin{equation}
  Ri_g(z)=\frac{N^2(z)}{\left(\mathrm{d}U/\mathrm{d}z\right)^2},
  \label{eq:gradient-richardson-number}
\end{equation}
where $U(z)$ is the mean streamwise velocity from
Eq.~\eqref{eq:fully-developed-channel-flow}. The numerator represents the
squared buoyancy frequency, while the denominator represents the squared mean
shear rate. Larger positive $Ri_g$ indicates stronger local buoyancy relative
to shear; it is distinct from a case-level friction Richardson number.

A friction Richardson number instead compares a characteristic buoyancy
acceleration $b_\star$ acting over the channel half-height with the wall-shear
velocity scale. Its generic scaling is
\begin{equation}
  Ri_\tau\sim\frac{b_\star h}{u_\tau^2},
  \label{eq:generic-friction-richardson-number}
\end{equation}
where $h$ and $u_\tau$ are defined in
Eq.~\eqref{eq:friction-scaling-quantities}. The precise definition of
$b_\star$ depends on the temperature difference or flux, gravity convention,
and scalar normalization. Consequently, the normalization used by the
Garc\'ia-Villalba--del {\'A}lamo reference and its mapping to BRINE must be
verified before Eq.~\eqref{eq:generic-friction-richardson-number} is replaced
by a project-specific equality \cite{garciaVillalbaDelAlamo2011}.

The dimensionless groups describe different physical balances.
$Re_\tau$ in Eq.~\eqref{eq:friction-scaling-quantities} compares wall-shear
and viscous scales, while $Pr$ in Eq.~\eqref{eq:prandtl-number} compares
momentum and thermal diffusivities. Richardson numbers compare buoyancy with
shear or wall-friction scales. For stable stratification, a Froude number may
be written generically as $Fr=U_c/(NL_c)$, where $N=\sqrt{N^2}$ and $U_c$ and
$L_c$ are stated characteristic velocity and length scales; it compares
inertial and buoyancy time scales. Any relationship between $Fr$ and a
Richardson number depends on using compatible scales.

The planned active benchmark uses $Re_\tau=180$, $Pr=0.7$, and
$Ri_\tau=120$ with stable thermal stratification. These are target parameters,
not completed simulation results. The expected physical signatures are reduced
core turbulence and weaker wall-normal mixing, but their occurrence must be
established from the computed statistics. Planned outputs include the mean
temperature profile and a temperature-field slice for identifying possible
wave-like structures, alongside the scalar statistics in
Eq.~\eqref{eq:scalar-validation-statistics}. The exact gravity direction, wall
temperatures, buoyancy coefficient, and $Ri_\tau$ input relation remain subject
to confirmation before the benchmark is configured.

\subsection{Internal Gravity Waves in Stably Stratified Channel Flow}
\label{sec:internal-gravity-waves}

Internal gravity waves are oscillatory motions supported by stable
stratification. When a fluid parcel is displaced along the direction opposite
to gravity, its density generally differs from that of its new surroundings.
The resulting buoyancy force acts as a restoring force when $N^2>0$ in
Eq.~\eqref{eq:brunt-vaisala-frequency}. The same stable buoyancy that permits
these waves also resists sustained wall-normal transport, so wave motion and
turbulence modification must be considered together in a stratified channel
\cite{pope2000,garciaVillalbaDelAlamo2011}.

Let $\mathbf{e}_s=-\mathbf{g}/g$ be the unit vector in the increasing-$s$
direction introduced in Subsection~\ref{sec:stable-thermal-stratification}, and
let $u_s'=\mathbf{u}'\mathbin{\cdot}\mathbf{e}_s$ be the corresponding velocity
fluctuation. A scalar buoyancy perturbation, positive in the $\mathbf{e}_s$
direction, is defined by
\begin{equation}
  b'=-\frac{g\rho'}{\rho_0}=g\alpha_T\theta',
  \qquad
  \mathbf{f}_b'=b'\mathbf{e}_s,
  \label{eq:internal-wave-buoyancy-perturbation}
\end{equation}
where $\rho'$ and $\theta'$ are the dimensional density and temperature
fluctuations, respectively. The second equality follows from
Eq.~\eqref{eq:boussinesq-density-temperature}, while the vector direction is
consistent with Eq.~\eqref{eq:boussinesq-buoyancy-acceleration}. If gravity is
wall-normal, $s$ is parallel or antiparallel to BRINE's wall-normal coordinate
$z$; it is not BRINE's spanwise coordinate $y$.

The elementary wave relation is obtained by linearising about a motionless,
inviscid, uniformly stratified Boussinesq state with constant $N^2>0$. The
perturbations are assumed small, incompressible, and unaffected by viscosity,
thermal diffusion, boundaries, mean shear, and nonlinear advection. Under
these idealisations, the dynamics along $s$ are
\begin{align}
  \frac{\partial u_s'}{\partial t}
    &=-\frac{1}{\rho_0}\frac{\partial p'}{\partial s}+b',
    \label{eq:linear-internal-wave-momentum}\\
  \frac{\partial b'}{\partial t}+N^2u_s'&=0,
    \label{eq:linear-internal-wave-buoyancy}
\end{align}
where $p'$ is the pressure perturbation. The second relation expresses the
restoring response: motion in the positive $s$ direction produces a negative
buoyancy perturbation. Combining these equations with incompressibility gives
the internal-wave equation
\begin{equation}
  \frac{\partial^2}{\partial t^2}
  \left(\boldsymbol{\nabla}^2u_s'\right)
  +N^2\boldsymbol{\nabla}_h^2u_s'=0,
  \label{eq:internal-gravity-wave-equation}
\end{equation}
where $\boldsymbol{\nabla}_h^2=\boldsymbol{\nabla}^2-
\partial^2/\partial s^2$ contains the two directions perpendicular to gravity.
This subscript denotes a gravity-horizontal operator and is unrelated to the
channel half-height $h$.

For a plane wave proportional to
$\exp[\mathrm{i}(\mathbf{k}_h\mathbin{\cdot}\mathbf{x}_h+ms-
\widehat{\omega}t)]$, Eq.~\eqref{eq:internal-gravity-wave-equation} yields
\begin{equation}
  \widehat{\omega}^{\,2}
  =N^2\frac{k_h^2}{k_h^2+m^2},
  \label{eq:internal-gravity-wave-dispersion}
\end{equation}
where $\mathbf{k}_h$ is the wavevector perpendicular to gravity,
$k_h=|\mathbf{k}_h|$, $m$ is the wavenumber along $s$, and
$\widehat{\omega}$ is the intrinsic angular frequency. Propagating oblique
internal waves therefore satisfy $0<|\widehat{\omega}|<N$. A wavevector that is
nearly perpendicular to gravity has $k_h\gg|m|$ and a frequency approaching
$N$, whereas a wavevector nearly parallel to gravity has
$k_h\ll|m|$ and a frequency approaching zero. These statements concern the
wavevector orientation, not the direction of phase or energy propagation.

In a channel with a streamwise mean velocity $U(z)$, an observed angular
frequency $\omega$ is Doppler shifted. A local intrinsic frequency may be
written
\begin{equation}
  \widehat{\omega}(z)=\omega-k_xU(z),
  \label{eq:internal-gravity-wave-doppler-shift}
\end{equation}
where $k_x$ is the streamwise wavenumber. Equations
\eqref{eq:internal-gravity-wave-dispersion} and
\eqref{eq:internal-gravity-wave-doppler-shift} are diagnostic guides rather
than an exact global dispersion relation for the present channel. The mean
shear and $N^2$ vary with $z$, and viscosity, thermal diffusion, nonlinear
interactions, and turbulence are absent from the ideal derivation.

The walls add a further restriction. The impermeability condition in
Subsection~\ref{sec:channel-flow-governing-equations} requires $w'=0$ at each
wall; when gravity is wall-normal, the same condition applies to $u_s'$ up to
its sign. Disturbances generated within the channel may propagate through the
stratified core, reflect from regions or boundaries that inhibit propagation,
or combine into standing patterns. Confinement can select discrete
wall-normal structures, but the admissible structures depend on the actual
mean profiles and boundary conditions and should not be inferred solely from
the uniform-$N$ model.

Internal waves exchange kinetic and buoyancy potential energy through the
buoyancy flux. They can carry coherent motion through a region where
wall-normal turbulent transport is weak, while wave shear, nonlinear
interaction, or wave breaking can transfer energy back to turbulence. Channel
studies report that internal-wave activity can coexist with near-wall
turbulence and become prominent in a buoyancy-dominated core
\cite{armenioSarkar2002,garciaVillalbaDelAlamo2011}. This coexistence does not
make every oscillation a gravity wave: advected turbulent eddies, intermittent
bursts, slow drift of the mean field, and numerical or sampling artefacts can
also produce wave-like patterns.

Evidence for an internal-wave interpretation should therefore combine several
diagnostics. Useful evidence includes coherent peaks in frequency--wavenumber
spectra, agreement of $\widehat{\omega}$ with its permitted range and with a
Doppler-shifted dispersion relation, a reproducible phase relationship between
$u_s'$ and $b'$ or $\theta'$, and a coherent wall-normal mode structure over a
documented time interval. Propagation, reflection, or standing-wave behaviour
should be distinguished where the data permit. A single instantaneous
temperature slice, a smooth mean profile, or oscillation at one probe is not
sufficient proof.

The planned $Re_\tau=180$, $Pr=0.7$, $Ri_\tau=120$ case is intended to test
for such behaviour; these remain target parameters and are not completed
results. Its interpretation must retain the distinction between the local
$Ri_g$ in Eq.~\eqref{eq:gradient-richardson-number} and the case-level
$Ri_\tau$ in Eq.~\eqref{eq:generic-friction-richardson-number}. Future
post-processing should retain time-resolved fields long enough for converged
frequency estimates, record the sampling interval and analysis window, and
examine frequency spectra, joint frequency--wavenumber spectra, phase
relationships, and wall-normal structure. Any comparison must document the
coordinate mapping, normalization, averaging window, folding or
symmetrisation, interpolation, and data provenance. Resulting spectra and
comparison figures must follow the repository's mandatory scientific plotting
standard, including its export and disclosure requirements. No wave detection
or validation is claimed at this theory checkpoint.

\subsection[Direct Numerical Simulation, Resolution, and Statistical Convergence]
{Direct Numerical Simulation, Resolution, and\\ Statistical Convergence}
\label{sec:dns-resolution-statistical-convergence}

\subsubsection{Direct Numerical Simulation}

Direct numerical simulation (DNS) solves the governing equations without a
turbulence model. In principle, the computational representation must capture
the large energy-containing motions, the intermediate inertial-range scales
through which energy is transferred, and the smallest dynamically relevant
dissipative motions. Reynolds-averaged Navier--Stokes methods instead model the
effects of all turbulent fluctuations on the mean flow, whereas large-eddy
simulation resolves the larger motions and models the unresolved subgrid
scales. DNS is therefore the most demanding of these approaches in spatial
resolution, temporal resolution, domain size, and sampling duration
\cite{pope2000}.

The absence of an active turbulence model is necessary but not sufficient for
a calculation to be described as adequately resolved DNS. The mesh must
resolve the relevant velocity and scalar scales, the time step must resolve
their evolution, the domain must contain the important large structures, and
the reported statistics must be converged. These requirements must be
demonstrated for the quantities of interest. The present discussion does not
assign a spatial discretisation, time-integration method, formal order of
accuracy, or dealiasing procedure to BRINE because those implementation
details have not yet been verified from the approved code or documentation.

\subsubsection{Dissipative Scales and Grid Spacing}

For locally isotropic turbulence, the characteristic smallest viscous length
scale is the Kolmogorov scale
\begin{equation}
  \eta=\left(\frac{\nu^3}{\varepsilon}\right)^{1/4},
  \label{eq:kolmogorov-length-scale}
\end{equation}
where $\eta$ is the Kolmogorov length, $\nu$ is the kinematic viscosity, and
$\varepsilon$ is the turbulent kinetic-energy dissipation rate per unit mass.
Their SI units are $\mathrm{m}$, $\mathrm{m^2\,s^{-1}}$, and
$\mathrm{m^2\,s^{-3}}$, respectively. The dissipation rate varies across a
wall-bounded flow, so strongly dissipative regions can contain a smaller
$\eta$ than a single global estimate suggests. Resolution should consequently
be assessed using the spatial distribution of dissipation where it is
available, rather than one unqualified domain-average value
\cite{pope2000}.

The smallest scalar scale need not equal the smallest velocity scale. For
$Pr$ greater than or comparable to unity, a commonly used estimate is the
Batchelor scale
\begin{equation}
  \eta_B=\frac{\eta}{\sqrt{Pr}},
  \label{eq:batchelor-length-scale}
\end{equation}
where $\eta_B$ is the scalar dissipative length and $Pr$ is defined in
Eq.~\eqref{eq:prandtl-number}. The applicability of
Eq.~\eqref{eq:batchelor-length-scale} depends on the scalar regime and is most
relevant when $Pr\gtrsim1$; it is not a universal scalar-resolution rule. The
planned $Pr=1$ and $Pr=0.7$ cases do not require an extended treatment of
high-$Pr$ scalar microstructure, but velocity and scalar resolution must still
be checked separately.

For uniform periodic grids in the wall-parallel directions, the nominal
spacings are
\begin{equation}
  \Delta x=\frac{L_x}{N_x},
  \qquad
  \Delta y=\frac{L_y}{N_y},
  \qquad
  \Delta z_j=z_{j+1}-z_j,
  \label{eq:nominal-grid-spacings}
\end{equation}
where $L_x$ and $L_y$ are the domain lengths, $N_x$ and $N_y$ are the numbers
of periodic grid points, and $z_j$ is the $j$th physical wall-normal point.
The local spacing $\Delta z_j$ is retained because a stretched wall-normal
grid is generally non-uniform. In wall units,
\begin{equation}
  \Delta x^+=\frac{\Delta x\,u_\tau}{\nu},
  \qquad
  \Delta y^+=\frac{\Delta y\,u_\tau}{\nu},
  \qquad
  \Delta z_j^+=\frac{\Delta z_j\,u_\tau}{\nu},
  \label{eq:grid-spacings-wall-units}
\end{equation}
where $u_\tau$ and $\nu/u_\tau$ are defined in
Eqs.~\eqref{eq:friction-scaling-quantities} and
\eqref{eq:viscous-length-wall-units}. The quantities $\Delta x^+$ and
$\Delta y^+$ characterise the nominal wall-parallel resolution, while
$\Delta z_j^+$ varies across the channel. Both its minimum near-wall value and
maximum core value should be reported.

The distance from the wall to the first physical grid point is not necessarily
the minimum cell width; the distinction depends on whether variables are
stored at nodes, cell centres, or staggered locations. Ghost nodes are
computational boundary devices and must not be counted as additional physical
resolution. Acceptable spacings depend on the numerical method, Reynolds
number, target statistic, and demonstrated grid convergence. Comparison with
published channel-DNS grids, such as the established $Re_\tau=590$ reference,
is useful context but does not replace a resolution or refinement assessment
\cite{moserKimMansour1999}.

\subsubsection{Domain Size and Wall-Normal Stretching}

A DNS domain must contain the important energy-containing motions as well as
the smaller scales resolved by the mesh. The streamwise length $L_x$ must
permit the long structures of the mean-flow direction, the spanwise length
$L_y$ must accommodate the relevant cross-stream organisation, and the
wall-normal length is the full channel height $L_z=2h$. The $x$ and $y$
directions are periodic according to Eq.~\eqref{eq:channel-periodicity}. Their
admissible wavenumbers are discrete,
\begin{equation}
  k_x=\frac{2\pi n_x}{L_x},
  \qquad
  k_y=\frac{2\pi n_y}{L_y},
  \qquad
  n_x,n_y\in\mathbb{Z},
  \label{eq:periodic-domain-wavenumbers}
\end{equation}
where $n_x$ and $n_y$ are integer mode indices. An undersized periodic domain
can therefore constrain large turbulent structures artificially.

Internal-wave analysis is also domain-sensitive. The domain and stored-field
resolution must permit the relevant wavelengths, as discussed in
Subsection~\ref{sec:internal-gravity-waves}. Periodicity restricts the
available streamwise and spanwise modes, while wall confinement restricts the
wall-normal structure. The planned domains have not yet been demonstrated to
be sufficient for either the largest turbulent structures or the relevant wave
modes \cite{armenioSarkar2002,garciaVillalbaDelAlamo2011}.

Channel grids commonly cluster points near the walls to resolve steep mean
velocity and scalar gradients and the thin viscous and conductive layers.
Stretching improves near-wall resolution without imposing the same fine
spacing throughout the channel and can reduce the total grid cost relative to
a uniformly fine mesh. It also has disadvantages: the smallest spacing can
restrict the time step, abrupt changes in spacing can reduce accuracy, and
wall-normal differentiation and interpolation require care. The mapping,
stretching factor, physical point count, and ghost-node treatment must
therefore be documented. No stretching formula is assumed here because the
BRINE mapping has not been verified.

The fresh Kleandro thermal setup has an unresolved stretching factor. Its
separate extended-restart record reports a factor of $2.0$, but this is a
setup record rather than a universal recommendation and must not be transferred
to a fresh project case without checking the approved inputs.

\subsubsection{Stability Restrictions and the Solver Time Step}

A generic multidimensional Courant number at a grid location is
\begin{equation}
  \mathrm{CFL}
  =\Delta t\left(
    \frac{|u|}{\Delta x}
    +\frac{|v|}{\Delta y}
    +\frac{|w|}{\Delta z_j}
  \right),
  \label{eq:multidimensional-cfl-number}
\end{equation}
where $\Delta t$ is the solver time step and $u$, $v$, and $w$ are the local
streamwise, spanwise, and wall-normal velocities. An explicit or partly
explicit method generally requires
$\mathrm{CFL}\leq C_{\mathrm{adv}}$, where $C_{\mathrm{adv}}$ is a
method-dependent advective stability limit. Its value depends on the actual
spatial and temporal discretisations and must be established for BRINE rather
than assumed. The estimate should use the maximum relevant local velocities,
the local $\Delta z_j$ on a stretched grid, and a safety margin; a universal
criterion $\mathrm{CFL}<1$ is not asserted.

Generic local measures of momentum and scalar diffusion are
\begin{align}
  D_{\nu,j}
  &=\nu\Delta t\left(
    \frac{1}{\Delta x^2}
    +\frac{1}{\Delta y^2}
    +\frac{1}{\Delta z_j^2}
  \right),
  \label{eq:viscous-diffusion-measure}\\
  D_{\kappa,j}
  &=\kappa\Delta t\left(
    \frac{1}{\Delta x^2}
    +\frac{1}{\Delta y^2}
    +\frac{1}{\Delta z_j^2}
  \right),
  \label{eq:scalar-diffusion-measure}
\end{align}
where $\kappa$ is the scalar diffusivity. Stability can require
$D_{\nu,j}\leq C_\nu$ and $D_{\kappa,j}\leq C_\kappa$, but the constants
$C_\nu$ and $C_\kappa$ are properties of the verified numerical scheme, not
physical constants. Both restrictions must be checked using the most
restrictive local spacing. Because $Pr=\nu/\kappa$, a case with $Pr<1$ has
$\kappa>\nu$ and scalar diffusion can impose the stronger explicit
restriction; for $Pr=1$, the two diffusivities are equal. The smallest
wall-normal spacing may dominate either estimate.

The usable solver time step must satisfy every applicable restriction,
\begin{equation}
  \Delta t\leq
  \min\left(
    \Delta t_{\mathrm{adv}},
    \Delta t_\nu,
    \Delta t_\kappa,
    \Delta t_{\mathrm{other}}
  \right),
  \label{eq:combined-time-step-restriction}
\end{equation}
where the terms denote the advective, viscous, scalar-diffusive, and other
solver-specific limits. A safety margin should be retained. No project time
step can be selected from these relations until the actual grid, velocity
range, treatment of diffusion, and BRINE scheme have been confirmed.

\subsubsection{Physical Temporal Resolution and Stored Output}

Numerical stability alone does not ensure adequate temporal resolution.
$\Delta t$ must also resolve turbulent evolution, near-wall dynamics, scalar
fluctuations, and any internal-wave oscillations of interest. The solver time
step is distinct from the restart or checkpoint interval. It also differs from
the instantaneous-field output interval and the interval between statistical
samples. Infrequent output can hide physical dynamics even when the solver
itself is stable.

If stored samples are separated by $\Delta t_s$, their Nyquist frequency is
\begin{equation}
  f_N=\frac{1}{2\Delta t_s},
  \label{eq:nyquist-frequency}
\end{equation}
where $f_N$ is measured in hertz for dimensional time and $\Delta t_s$ is the
sampling interval between stored data. Frequencies above $f_N$ cannot be
resolved correctly and may be aliased into lower frequencies. Meaningful
internal-wave spectra therefore require output frequent enough for the
expected frequency range, while the total sampling duration must be long
enough for the lowest frequency of interest. No output interval is selected at
this checkpoint.

\subsubsection{Transients, Stationarity, and Averaging}

Numerical convergence and statistical stationarity are different
requirements. A time step may remain stable, and any iterative solver may
meet its numerical tolerance, while the evolving turbulent statistics still
depend on the initial condition. A turbulent calculation normally passes
through an initial transient, an approach to statistically stationary
behaviour, and a production interval used for reported statistics. The
initial transient should not normally be included in production averages
unless transient physics is itself the subject of study.

Stationarity can be assessed using histories of bulk velocity or mass flow,
pressure-gradient forcing, wall shear stress, friction velocity, total kinetic
energy, scalar mean or variance, wall scalar flux, spatially averaged
temperature, and relevant buoyancy quantities. The useful set depends on the
case and its forcing. No single flat-looking history proves stationarity;
several quantities and more than one portion of the record should be examined.

The ideal time average in Eq.~\eqref{eq:turbulence-time-average} is replaced in
finite data by
\begin{equation}
  \langle\phi\rangle_T
  =\frac{1}{T}\int_{t_0}^{t_0+T}\phi(t)\,\mathrm{d}t,
  \label{eq:finite-production-time-average}
\end{equation}
where $t_0$ is the beginning of the production window and $T$ is its duration.
For the channel, plane averaging over the statistically homogeneous $x$ and
$y$ directions gives the space--time average in
Eq.~\eqref{eq:channel-space-time-average} and can increase the effective
sample size. Consecutive stored fields can nevertheless be correlated.
Consequently, the number of effectively independent samples is controlled by
the production duration relative to the integral correlation time, not simply
by the number of output files \cite{pope2000}.

\subsubsection{Statistical and Numerical Convergence Checks}

Practical statistical checks include comparing profiles from successive parts
of the production window, examining cumulative or running means, and testing
whether changes become small relative to the intended accuracy. Independent
time intervals should be compared where possible, and sampling uncertainty
should be reported. Lower- and upper-wall symmetry is a useful diagnostic only
when the forcing, boundary conditions, and expected physics justify that
symmetry; it must not be imposed automatically.

Statistical convergence, grid convergence, time-step convergence, and
agreement with reference DNS address different questions. Statistical
convergence concerns sampling uncertainty, grid convergence concerns spatial
discretisation error, and time-step convergence concerns temporal
discretisation error. Agreement with a reference tests the combined outcome
for compatible cases, but does not by itself prove any of the other three.
For thermal and stratified calculations, convergence should be assessed
separately for mean velocity, the three RMS velocity components, Reynolds
shear stress, mean scalar, scalar RMS, turbulent scalar flux, wall flux or wall
gradient, and any wave-related spectra. These quantities extend the turbulence
and scalar statistics defined in
Eqs.~\eqref{eq:rms-velocity-fluctuations},
\eqref{eq:reynolds-shear-stress}, and
\eqref{eq:scalar-validation-statistics}.

A credible sensitivity assessment may compare a baseline mesh with a refined
mesh and, where appropriate, repeat a case with a reduced $\Delta t$. The
physical parameters must be held fixed, integral quantities and profiles
should both be compared, and every numerical setting that changes should be
recorded. This separation helps distinguish physical differences from
numerical ones. A full refinement campaign is not prescribed here; the
feasible strategy will depend on the selected benchmark, Leonardo resource
cost, and advisor approval. Future convergence histories and comparison
figures must follow the repository's mandatory scientific plotting standard
and disclose normalization, averaging windows, coordinate mapping,
interpolation, and any folding or symmetrisation.

\subsubsection{Application to the Planned Project Cases}

The planned sequence uses the friction Reynolds number defined in
Eq.~\eqref{eq:friction-scaling-quantities}. It consists of an unstratified
channel benchmark at $Re_\tau=590$, a passive-scalar benchmark at $Pr=1$, and
a stably stratified case at $Re_\tau=180$, $Pr=0.7$, and $Ri_\tau=120$. The
passive-scalar Reynolds number remains subject to confirmation because the
project records contain an unresolved $Re_\tau=550$ versus $Re_\tau=500$
inconsistency. All values are targets for future work, not completed
simulations.

Before any case is launched, the project must confirm the physical grid
dimensions, domain lengths, wall-normal stretching, physical and ghost-node
counts, viscosity, thermal diffusivity, solver time step, scheme-specific
stability limits, output and restart intervals, restart mode, production
averaging window, retained statistics, and compatibility of the reference
dataset. The actual BRINE inputs and numerical scheme must be inspected before
final numerical values are assigned. In particular, the earlier $16^3$
attempt failed during setup before producing a simulation result and therefore
validated neither the solver nor its numerical resolution.
